An introduction to Docker for reproducible research, with examples from the R environment

### 2014-09-19 docker-paper/manuscript.Rmd
tweaking reference formatting

<!-- A wide range of proposals, I focus on those at the operating system level -->
Though a wide variety of approaches exists to work around these challenges,
few operate on a low enough level to provide a general solution.  [@Clark_2014]
provide an excellent description of this situation:

@@

[@Dudley_2010] gives several reasons that such comprehensive workflow
systems have not been more successful:

@@

In short, workflow software expects a new approach to computational research. 
In contrast, virtual machines (VMs) offer a more direct approach. Since
the computer Operating System (OS) already provides the software layer
responsible for coordinating all the different elements running on the computer,
the VM approach captures the OS and everything running on it whole-cloth.
To make this practical, [@Dudley_2010] and [@Howe_2012]
propose using virtual machine images that will run on the cloud, such as Amazon's
EC2 system, which is already based upon this kind of virtualization.

>>>>

<!-- A wide range of proposals, I focus on those at the operating system level -->
Though a wide variety of approaches exists to work around these challenges,
few operate on a low enough level to provide a general solution. Clark _et al._ [@Clark_2014]
provide an excellent description of this situation:

@@

Dudley & Butte [@Dudley_2010] give several reasons that such comprehensive workflow
systems have not been more successful:

@@

In short, workflow software expects a new approach to computational research. 
In contrast, virtual machines (VMs) offer a more direct approach. Since
the computer Operating System (OS) already provides the software layer
responsible for coordinating all the different elements running on the computer,
the VM approach captures the OS and everything running on it whole-cloth.
To make this practical, Dudley & Butte [@Dudley_2010] and Howe [@Howe_2012] both
propose using virtual machine images that will run on the cloud, such as Amazon's
EC2 system, which is already based upon this kind of virtualization.
